Master's Research Proposal

### 2024-05-30 proposal/Proposal.tex
breaking up the lit review work
better title page
navigating the document

\title{Master's Thesis Proposal}
\author{Marcel Gietzmann-Sanders}
\date{}
\setcounter{tocdepth}{2}
\begin{document}
\maketitle
\tableofcontents
\newpage

@@

>>>>

\makeatletter
\renewcommand{\maketitle}{
\begin{center}

\pagestyle{empty}
\phantom{.}  %necessary to add space on top before the title
\vspace{3cm}

{\Huge \bf \@title\par}
\vspace{2.5cm}

{\LARGE Marcel Gietzmann-Sanders}\\[1cm]

{\Large\@date}

\vspace{2.5cm}
{\Large Dr. Andrew Seitz}\hspace{2cm}{\Large Dr. Curry Cunningham}\\[2cm]{\Large Michael Courtney, M.S.}\\[2cm]
College of Fisheries and Ocean Sciences\\
University of Alaska Fairbanks

\end{center}
}\makeatother

\title{Master's Research Proposal}

\date{2024}
\setcounter{tocdepth}{2}
\begin{document}
\maketitle
\newpage

\section{Navigating This Document}

This document is organized in order to allow you, the reader, to read as little or as much as you need/want. \newline

It begins with the \textbf{objectives} so that you know immediately exactly what this proposal is hoping to achieve and whether this is of interest to you.  \newline

Then it dives into how we will go about demonstrating success along those objectives, this will inform you on the specific \textbf{outcomes} to be expected. \newline

Finally there is a \textbf{timeline} provided to give a sense of when these outcomes can be expected. \newline

If these are compelling enough there is no need to read any further. \newline

However if you are interested in the rationales behind these objectives or diving into related work has already been done by others, the \textbf{Rationales} and \textbf{Related Work} sections are for you.

\tableofcontents
\newpage

@@

\subsection{Chinook Ecology}

\subsection{Chinook Management}

\subsection{Studies Using PSAT Data}

\subsection{Spatial Modeling}

\subsection{Spatial Management}
